---
title: "Season Repeats Data Preparation"
author: "R-Walmsley"
date: "20/10/21"
output: 
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages
```{r}
library(data.table)
```

```{r, include = FALSE}
d <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat0_five_sec_basic_summary.csv")))
red <- colnames(d)
for (day in c("mon", "tue", "wed", "thur", "fri", "sat", "sun")){
  red <- red[!(grepl(day,red))]
}
red <- red[!(grepl("hour",red))]
red <- red[!(grepl("hrs",red))]
red <- red[!(grepl("MET",red))]
red <- red[!(grepl("eid",red))]
red <- red[!(grepl("calibration",red))]
behaviours <- c("^MVPA", "light", "sedentary", "sleep")

for (day in behaviours){
  red <- red[!(grepl(day,red))]
}
red <- c(red, "extremeAcc", "tooManyClips", "excluded")
print(red)

```

## Load data and perform exclusions
```{r}
# Note preprepared list of column names for inclusion in the final data
print(red)

# Load and prpeare datasets
for (i in 0:4){
  
  # Load data
  d <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat", i, "_five_sec_basic_summary.csv")))
  wa1 <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat", i, "_walmsley_summary.csv")))
  w1 <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat", i, "_willetts_full_summary.csv")))
  w2 <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat", i, "_willetts_reduced_summary.csv")))
  
  # Set up data frame to record exclusions
  exclusions <- data.frame(matrix(nrow = 0, ncol = 2))
  colnames(exclusions) <- c("Category", "n")
  
  # Overall numbers
  exclusions <- rbind(exclusions, data.frame("Category" = "Total_participants", "n" = nrow(d)))
  
  # Calibration 
  exclusions <- rbind(exclusions, data.frame("Category" = "Not_calibrated", "n" = sum(d$quality.goodCalibration == 0)))
  
  # Wear time 
  exclusions <- rbind(exclusions, data.frame("Category" = "Insufficient_wear_time", "n" = sum(d$quality.goodWearTime == 0)))
  
  # Extreme acc values
  d$extremeAcc <- (d$acc.overall.avg > 100)
  exclusions <- rbind(exclusions, data.frame("Category" = "Extreme_acc_values", "n" = sum(d$extremeAcc)))
  
  # Clips before or after calibration
  d$tooManyClips <- (d$clipsAfterCalibration > 0.01*d$totalReads)|(d$clipsBeforeCalibration > 0.01*d$totalReads)
  exclusions <- rbind(exclusions, data.frame("Category" = "Too_many_clips", "n" = sum(d$tooManyClips)))
    
  # Excluded in (any Category)
  d$excluded <- (!(d$quality.goodCalibration))|(!(d$quality.goodWearTime))|(d$extremeAcc)|(d$tooManyClips)
  exclusions <- rbind(exclusions, data.frame("Category" = "Excluded_for_any_reason", "n" = sum(d$excluded)))
  
  # Write one dataset per repeat
  colnames(d) <- paste0(colnames(d), "_s", i)
  colnames(wa1) <- paste0(colnames(wa1), "_s", i)
  colnames(w1) <- paste0(colnames(w1), "_s", i)
  colnames(w2) <- paste0(colnames(w2), "_s", i)
  
  d$eid <- gsub(paste0("_90001_", i, "_0.gz"), "", d[, paste0("eid_s", i)])
  wa1$eid <- gsub(paste0("_90001_", i, "_0.gz"), "", wa1[, paste0("eid_s", i)])
  w1$eid <- gsub(paste0("_90001_", i, "_0-epoch.csv.gz"), "", w1[, paste0("eid_s", i)])
  w2$eid <- gsub(paste0("_90001_", i, "_0-epoch.csv.gz"), "", w2[, paste0("eid_s", i)])
  
  # Store datasets at this point 
  assign(paste0("c", i), d)
  assign(paste0("wa", i), wa1)
  assign(paste0("wo", i), w1)
  assign(paste0("wr", i), w2)
  
  # Relabel behaviours
  behaviours <- c("MVPA", "light", "sedentary", "sleep")
  wa1_mini <- as.data.frame(wa1[, c("eid")])
  colnames(wa1_mini) <- "eid"
  for (name in behaviours){
    wa1_mini[, paste0(name, "_ML4_red_s", i) ] <- wa1[, paste0(name, ".overall.avg_s", i)]
  }

  
  behaviours <- c("bicycling", "vehicle", "sit.stand", "sleep", "mixed", "walking")
  w1_mini <- as.data.frame(w1[, c("eid")])
  w2_mini <- as.data.frame(w2[, c("eid")])
  colnames(w1_mini) <- "eid"
  colnames(w2_mini) <- "eid"
  for (name in behaviours){
    w1_mini[, paste0(name, "_ML6_full_s", i) ] <- w1[, paste0(name, ".overall.avg_s", i)]
    w2_mini[, paste0(name, "_ML6_red_s", i) ] <- w2[, paste0(name, ".overall.avg_s", i)]
  }
  
  # Keep only relevant columns
  d <- d[, c("eid", paste0(red, "_s", i))]
  
  # Merge data 
  d <- merge(d, wa1_mini, by = "eid")
  d <- merge(d, w1_mini, by = "eid")
  d <- merge(d, w2_mini, by = "eid")
  
  # Write combined data
  assign(paste0("d", i), d)
  
  # Write table describing 
  names(exclusions)[names(exclusions) == 'n'] <- paste0("n_s", i)
  assign(paste0("exclusions", i), exclusions)
}

# Collate table describing exclusions
exclusions <- exclusions0
 for (i in 0:4){
   exclusions <- merge(exclusions, get(paste0("exclusions", i)), by = "Category", sort = FALSE)
 }
```

Table describing exclusions at each repeat:

```{r}
exclusions
```

## Join files
```{r}
# Join files
dAll <- d0
for (i in 1:4){
  dAll <- merge(dAll, get(paste0("d", i)), by = "eid", all = TRUE)
}
# Add indicator of data and of high quality data at all repeats
dAll$data_for_all_repeats <- !(is.na(dAll$excluded_s0) | is.na(dAll$excluded_s1) |is.na(dAll$excluded_s2)| is.na(dAll$excluded_s3)| is.na(dAll$excluded_s4))
dAll$quality_data_for_all_repeats <- (dAll$data_for_all_repeats) & !(dAll$excluded_s0 | dAll$excluded_s1 | dAll$excluded_s2 | dAll$excluded_s3 | dAll$excluded_s4)
             
```

## Summarise data
There are:

- `r nrow(dAll)` participants in at least one repeat
- `r sum(dAll$data_for_all_repeats, na.rm = TRUE)` participants with data for all repeats (including baseline)
- `r sum(dAll$quality_data_for_all_repeats, na.rm = TRUE)` participants with high-quality data for all repeats (including baseline)


## Write file
```{r}
saveRDS(dAll, "data/59070/prepped_repeat_data_with_5sec_epoch_oct21.RDS")
write.csv(dAll, "data/59070/summary_data_all_with_5sec_epoch_and_ml_oct21.csv")
```

## Compare with previous version of same data 
This is a sanity check to check correctness of processing
```{r}
old <- readRDS("../seasonRepeatsMar20/data/59070/prepped_repeat_data_with_5sec_epoch.RDS")

merged <- merge(dAll, old, by = "eid")
for (i in 0:4){
  for (col in c("acc.overall.avg", "sleep_ML6_full", "sit.stand_ML6_red", "light_ML4_red")){
    print(paste0("Column:", col))
    print(paste0("Repeat:", i))
    mini <-  merged[!(is.na(merged[, paste0(col, "_s", i, ".x")])), ]
    print(head(mini[(mini[, paste0(col, "_s", i, ".x")] != mini[, paste0(col, "_s", i, ".y")]), paste0(col, "_s", i, c(".x", ".y"))]))
    n_mismatched <- nrow(mini[(mini[, paste0(col, "_s", i, ".x")] != mini[, paste0(col, "_s", i, ".y")]), ])
    print(paste0(n_mismatched, " non-NA mismatched rows"))
    print("Distribution of differences:")
    diffs <- mini[, paste0(col, "_s", i, ".x")] - mini[, paste0(col, "_s", i, ".y")]
    #print(hist(diffs))
    print(quantile(diffs, seq(0, 1, by = 0.2), na.rm = TRUE))
  }
}
```

IMPORTANT NOTE: the final file contains a few apparently erroneous s1 files. These are files where the s1 occurs long before the actual repeated measurements study (and so may be an additional baseline measurement or some kind of matching failure. )
