---
title: "Season Repeats Data Preparation"
author: "R-Walmsley"
date: "2023-01-11"
output: 
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages
```{r}
library(data.table)
```

This chunk is just to get a set of columns of relevance: 
```{r, include = FALSE}
d <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat0_five_sec_basic_summary.csv")))
red <- colnames(d)
for (day in c("mon", "tue", "wed", "thur", "fri", "sat", "sun")){
  red <- red[!(grepl(day,red))]
}
red <- red[!(grepl("hour|hrs|MET|calibration|CutPoint|eid",red))]
red <- c(red, "extremeAcc", "tooManyClips", "excluded")
print(red)
rm(d)
```

## Load data and perform exclusions
```{r}
# Note preprepared list of column names for inclusion in the final data
print(red)

# Load and prpeare datasets
for (i in 0:4){
  
  # Load data
  d <- data.frame(fread(paste0("data/59070/summary_files_oct21/oct21_repeat", i, "_five_sec_basic_summary.csv")))

  # Set up data frame to record exclusions
  exclusions <- data.frame(matrix(nrow = 0, ncol = 2))
  colnames(exclusions) <- c("Category", "n")
  
  # Overall numbers
  exclusions <- rbind(exclusions, data.frame("Category" = "Total_participants", "n" = nrow(d)))
  
  # Calibration 
  exclusions <- rbind(exclusions, data.frame("Category" = "Not_calibrated", "n" = sum(d$quality.goodCalibration == 0)))
  
  # Wear time 
  exclusions <- rbind(exclusions, data.frame("Category" = "Insufficient_wear_time", "n" = sum(d$quality.goodWearTime == 0)))
  
  # Extreme acc values
  d$extremeAcc <- (d$acc.overall.avg > 100)
  exclusions <- rbind(exclusions, data.frame("Category" = "Extreme_acc_values", "n" = sum(d$extremeAcc)))
  
  # Clips before or after calibration
  d$tooManyClips <- (d$clipsAfterCalibration > 0.01*d$totalReads)|(d$clipsBeforeCalibration > 0.01*d$totalReads)
  exclusions <- rbind(exclusions, data.frame("Category" = "Too_many_clips", "n" = sum(d$tooManyClips)))
    
  # Excluded in (any Category)
  d$excluded <- (!(d$quality.goodCalibration))|(!(d$quality.goodWearTime))|(d$extremeAcc)|(d$tooManyClips)
  exclusions <- rbind(exclusions, data.frame("Category" = "Excluded_for_any_reason", "n" = sum(d$excluded))) # Note the individual categories for exclusion are not mutually exclusive
  
  # Rename columns
  colnames(d) <- paste0(colnames(d), "_s", i)
  d$eid <- gsub(paste0("_90001_", i, "_0.gz"), "", d[, paste0("eid_s", i)])
  
  # Keep only a subset of columns 
  d <- d[, c("eid", paste0(red, "_s", i))]
  
  # Store dataset at this point 
  assign(paste0("d", i), d)
 
  # Write table describing 
  names(exclusions)[names(exclusions) == 'n'] <- paste0("n_s", i)
  assign(paste0("exclusions", i), exclusions)
}
```

Table describing exclusions at each repeat:

```{r}
# Collate table describing exclusions
exclusions <- exclusions0
 for (i in 0:4){
   exclusions <- merge(exclusions, get(paste0("exclusions", i)), by = "Category", sort = FALSE)
 }

exclusions
```

## Join files
```{r}
# Join files
dAll <- d0
for (i in 1:4){
  dAll <- merge(dAll, get(paste0("d", i)), by = "eid", all = TRUE)
}
# Add indicator of data and of high quality data at all repeats
dAll$data_for_all_repeats <- !(is.na(dAll$excluded_s0) | is.na(dAll$excluded_s1) |is.na(dAll$excluded_s2)| is.na(dAll$excluded_s3)| is.na(dAll$excluded_s4))
dAll$quality_data_for_all_repeats <- (dAll$data_for_all_repeats) & !(dAll$excluded_s0 | dAll$excluded_s1 | dAll$excluded_s2 | dAll$excluded_s3 | dAll$excluded_s4)
```

## Summarise data
There are:

- `r nrow(dAll)` participants in at least one repeat
- `r sum(dAll$data_for_all_repeats, na.rm = TRUE)` participants with data for all repeats (including baseline)
- `r sum(dAll$quality_data_for_all_repeats, na.rm = TRUE)` participants with high-quality data for all repeats (including baseline)

## Write file
```{r}
write.csv(dAll, "data/59070/summary_data_all_with_5sec_epoch_and_ml_jan23.csv")
```
